Manuscript progress report

### 2024-08-08 Docs/manuscript.Rmd
sampling quantiles
investigate the prediction interval

pred_list_GLMMad <- lapply(pred_list_GLMMad, function(x){
  colnames(x) <- name_vec
  return(x)
})

@@

>>>>

pred_list_GLMMad <- pred_list_GLMMad[1:5]
pred_list_GLMMad <- lapply(pred_list_GLMMad, function(x){
  colnames(x) <- name_vec
  return(x)
})

@@

For the fGFPCA method, which interval should we use? Sampling quantile would cross zero and the coverage rate seems to fluctuate a lot.

## A closer look at confidence/credible interval

Since using the true parameters did not change the results, I don't think ignoring prior variance made a huge difference. If we plot the variance of mean (from global bam) or the variance of estimated $\eta$, the trend would in fact be roughly cyclic.

I am not sure how to take into account the prior variation. As below:

$$Var(\hat{\eta}(t)) = Var(\hat{\mu}_0(t)+
\sum_k \hat{\phi}_k(t)
\hat{\xi}_k)$$

$$
\begin{aligned}
Var(\hat{\eta}(t) | \hat{\mu}_0(t), \hat{\lambda}_k, \hat{\phi}_k(t)) & = Var(\hat{\mu}_0(t))+
Var(\sum_k \hat{\phi}_k(t)
\hat{\xi}_k)\\

& = Var(\hat{\mu}_0(t))+ \sum_k \hat{\phi}_k^2(t)
\hat{\lambda}_k
\end{aligned}
$$

Not sure why we need to take into account the variation of mean function (from global BAM).

If we want to get rid of the conditions (let's for now assume the terms are independent):

$$Var(\hat{\eta}(t))  = Var(\hat{\mu}_0(t))+
Var(\sum_k \hat{\phi}_k(t)
\hat{\xi}_k)$$

The second term would be difficult to calculate. Is the estimated mean and variance of basis functions available?
